\documentclass[12pt]{article}
\usepackage{times}
\begin{document}
\newcommand{\problem}[1]{\underline{\Large \bf #1}}
\renewcommand{\section}[1]{\bigskip\underline{\bf #1}\\}
\newcommand{\header}[1]{\underline{\bf #1}}
\setlength{\parindent}{0.0in}
\setlength{\parskip}{1ex}

\problem{Word Order Reverser}

Thompson Tommy is a well known pop poet who specializes
in word-reversed poetry.  This is poetry in which the
words in each line are presented in reverse order, but
the punctuation is left in place.

For example, one of his poems is
\begin{center}\begin{tabular}{l}
moon! full the oh! \\
swoon to me leads \\
loon a of song the for! \\
\end{tabular}\end{center}

Not everyone can stomach this, and you have been asked
to write a translator which will render Thompson Tommy's
poems readable.


\section{Input}
You are being asked to translate a sequence of lines,
each no longer than 80 characters.
There may be blank lines.  Input ends with an end of file.


\section{Output}
For each line output that line exactly as is but with
word substitutions, and only word substitutions.  The
last word is substituted for the first, the next to last
for the second, and so forth, until the first is
substituted for the last.  Only words are to be substituted;
spaces and punctuation are to be left as is.  A word is
defined as a sequence of letters, containing
NO non-letters.  Letters may be lower or upper case.
A blank line translates to a blank
line.

\begin{center}
\begin{tabular}{l|l}
\begin{minipage}{2.4in}
\small
\header{Sample Input}
\begin{verbatim}
moon! full the oh!
swoon to me leads
loon a of song the for!

george there, hi!
phil there, bye!
is it, switch friend

**   rung+is-bell^the   !!
**   sung+is-song^the   !!
**      fun++++what     !!
\end{verbatim}
\end{minipage}\hspace*{0.1in}
&
\hspace*{0.1in}\begin{minipage}{2.4in}
\small
\header{Sample Output}
\begin{verbatim}
oh! the full moon!
leads me to swoon
for the song of a loon!

hi there, george!
bye there, phil!
friend switch, it is

**   the+bell-is^rung   !!
**   the+song-is^sung   !!
**      what++++fun     !!
\end{verbatim}
\end{minipage}
\end{tabular}
\end{center}

\bigskip

\begin{tabular}{ll}
Author:	      & Bob Walton $<$walton@seas.harvard.edu$>$ \\
Date:         & Sat Dec  1 22:26:28 EST 2012
\end{tabular}

The authors have placed this problem in the public domain;
they make no warranty and accept no liability for this problem.

\end{document}
